---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  warning = FALSE,
  eval = FALSE,
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# StockDistFit

<!-- badges: start -->
[![R-CMD-check](https://github.com/njuguna-brian/StockDistFit/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/njuguna-brian/StockDistFit/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of StockDistFit is to provide functions that help in fitting probability distributions to financial data, specifically stock returns and prices. These functions can be used to compare the goodness of fit of different distributions and choose the most appropriate one, which can aid in making investment decisions or modeling financial phenomena. The package also includes function for cumulative wealth generated over time, given the initial wealth. Overall, StockDistFit aims to simplify the process of fitting and analyzing probability distributions for financial data.

## Installation

You can install the development version of StockDistFit from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("njuguna-brian/StockDistFit")
```

## Example

An example is the following 

```{r example}
library(StockDistFit)
df <- asset_loader("path/to/data/folder", "AAPL", "Close")
df_returns <- weekly_return(df)

# Fit a normal Distribution to the Closing Price
norm_fit(df_returns)

```

